Visualizing demographic evolution using geographically inconsistent census data

### 2019-10-26 paper/intro.tex
final version paper piccard 1.0

We start by presenting an intuitive example of our representation in
Section~\ref{sec:introduction}, then we review the relevant literature on
longitudinal studies, data representation, clustering and regionalisation, and
spatio-temporal visualisation in Section~\ref{sec:related}. Our methodology is
introduced in detail in Section~\ref{sec:method}, along with the included
interface. Illustrative scenarios for Chicago and Toronto are presented in
Section~\ref{sec:study} and the feedback of five field experts are summarised in
Section~\ref{sec:expert}. Our prototype system is available at
\censure{\url{http://uoft.me/piccard}}, including more than forty regions in the
US and Canada. The source code is publicly available at
\censure{\url{https://github.com/fabioasdias/piccard}}.\footnote{The editors are
considering, at our request, an exception to the double-blind requirement to
allow access to the system. We provided them with the URLs of the system, code,
and documentation separately.}

@@

\begin{figure}
    \centering 
    \subfloat{
        \includegraphics[width=0.475\linewidth]{intuition.png}
    }
    \subfloat{
        \begin{tikzpicture}
            \node (push) at (-2,0) {};
            \node [circle, draw=red, thick] (a) at (0,4) {A};
            \node [circle, draw=green, thick] (b) at (4,4) {B};
            \node [circle, draw=blue,  thick] (c) at (0,2) {C};
            \node [circle, draw=red, thick] (d) at (2,2) {D};
            \node [circle, draw=green, thick] (e) at (4,2) {E};
            \node [circle, draw=blue, thick] (f) at (0,0) {F};
            \node [circle, draw=red, thick] (g) at (2,0) {G};
            \node [circle, draw=green, thick] (h) at (4,0) {H};
            \draw (a) -- (c);
            \draw (a) -- (b);
            \draw (a) -- (d);
            \draw (b) -- (e);
            \draw (c) -- (f);
            \draw (c) -- (d);
            \draw (d) -- (f);
            \draw (d) -- (e);
            \draw (d) -- (g);
            \draw (e) -- (h);
            \draw (f) -- (g);
            \draw (g) -- (h);
        \end{tikzpicture}
    } \caption{Network based spatio-temporal data representation. \textbf{Left}:
    Three temporal stages of the evolution of a fictitious urban area, with
    aggregation areas A to H. \textbf{Right}: Network representation of the
    aggregation areas where the colours identify similar regions.
        \label{fig:intuition}}
\end{figure}

>>>>

We start by presenting an intuitive example of our representation in
Section~\ref{sec:introduction}, then we review the relevant literature on
longitudinal studies, data representation, clustering and regionalisation, and
spatio-temporal visualisation in Section~\ref{sec:related}. Our methodology is
introduced in detail in Section~\ref{sec:method}, along with the included
interface. Illustrative scenarios for Chicago and Toronto are presented in
Section~\ref{sec:study} and the feedback of five field experts are summarised in
Section~\ref{sec:expert}. Our prototype system is available at
\url{http://uoft.me/piccard}, including more than forty regions in the US and
Canada. The source code is publicly available at
\url{https://github.com/fabioasdias/piccard}.

@@

\begin{figure}
    \centering 
    \subfloat{
        \includegraphics[width=0.475\linewidth]{intuition.png}
    }
    \subfloat{
        \begin{tikzpicture}[scale=0.75, every node/.style={scale=0.75}]
            \node (push) at (-2,0) {};
            \node [circle, draw=red, thick] (a) at (0,4) {A};
            \node [circle, draw=green, thick] (b) at (4,4) {B};
            \node [circle, draw=blue,  thick] (c) at (0,2) {C};
            \node [circle, draw=red, thick] (d) at (2,2) {D};
            \node [circle, draw=green, thick] (e) at (4,2) {E};
            \node [circle, draw=blue, thick] (f) at (0,0) {F};
            \node [circle, draw=red, thick] (g) at (2,0) {G};
            \node [circle, draw=green, thick] (h) at (4,0) {H};
            \draw (a) -- (c);
            \draw (a) -- (b);
            \draw (a) -- (d);
            \draw (b) -- (e);
            \draw (c) -- (f);
            \draw (c) -- (d);
            \draw (d) -- (f);
            \draw (d) -- (e);
            \draw (d) -- (g);
            \draw (e) -- (h);
            \draw (f) -- (g);
            \draw (g) -- (h);
        \end{tikzpicture}
    } \caption{Network based spatio-temporal data representation. \textbf{Left}:
    Three temporal stages of the evolution of a fictitious urban area, with
    aggregation areas A to H. \textbf{Right}: Network representation of the
    aggregation areas where the colours identify similar regions.
        \label{fig:intuition}}
\end{figure}
